Supervised Reinforcement Learning with Partial States: \\ a Teaching Method for Action Selection for HRI

### 2017-07-26 paper.tex
Reorder for image position

An example of an application is a social robot which interacts with children in an educational scenario.
The robot plays an educational game with children to teach them notions about
diverse topics according to the needs of the teacher. For this example, a child
and a robot are playing a game about the food web, teaching wich animals eat which
ones on a Sandtray~\cite{baxter2012touchscreen} as shown in
Figure~\ref{fig:game}. In addition to the child and
the robot, an adult supervises the robot using a tablet with a Graphical User
Interface (GUI) (Figure~\ref{fig:gui}) to teach the robot how to interact with the child.
\begin{figure}
        \centering
  \includegraphics[width=80mm]{./fig/game.png} 
    \caption{Game displayed on the Sandtray the child is playing with the robot.}
        \label{fig:game}
\end{figure}

As shown in Figures \ref{fig:game} and \ref{fig:gui}, the GUI is an augmented
version of the game itself, which can be use to make the robot move items on the
game by dragging them on the GUI or which can display actions proposed by the
robot with a cancel button to refuse an action. For example in
Figure~\ref{fig:gui} the robot proposes to move the eagle to the rat, and
highlight (as shown by blue circles) the eagle and the rat. This indicate that
features relevant to the eagle and the rat have been used to select this action.
\begin{figure}
        \centering
    \includegraphics[width=80mm]{./fig/proposition.png}
    \caption{Interface for the supervisor with an action being proposed, moving
        the eagle to the rat with highlight of the eagle and the rat.}
        \label{fig:gui}
\end{figure}

In the current implementation, the state is defined by the distance between each
animal and their life. With these features selected, the partial state
transmitted to the user is the distance between the eagle and the rat, the eagle's life and
the rat's life. Similarly, when selecting an action, the supervisor can 
select features in the state relevant to the action.

>>>>

An example of an application is a social robot which interacts with children in an educational scenario.
The robot plays an educational game with children to teach them notions about
diverse topics according to the needs of the teacher. For this example, a child
and a robot are playing a game about the food web, teaching wich animals eat which
ones on a Sandtray~\cite{baxter2012touchscreen}. In addition to the child and
the robot, an adult supervises the robot using a tablet with a Graphical User
Interface (GUI) to teach the robot how to interact with the child as shown in
Figure~\ref{fig:setup}.
\begin{figure}
        \centering
  \includegraphics[width=60mm]{./figs/setup} 
    \caption{Interaction setup: the child and the robot are interacting on the
    touchscreen and a supervisor can control the robot using a GUI on a tablet.}
        \label{fig:setup}
\end{figure}

The GUI (shown in Figure \ref{fig:gui} is an augmented
version of the game itself, which can be use to make the robot move items on the
game by dragging them on the GUI or which can display actions proposed by the
robot with a cancel button to refuse an action. For example in
Figure~\ref{fig:gui} the robot proposes to move the eagle to the rat, and
highlight (as shown by blue circles) the eagle and the rat. This indicate that
features relevant to the eagle and the rat have been used to select this action.

In the current implementation, the state is defined by the distance between each
animal and their energy. With these features selected, the partial state
transmitted to the user is the distance between the eagle and the rat, the
eagle's energy and
the rat's energy. Similarly, when selecting an action, the supervisor can 
select features in the state relevant to the action.

\begin{figure}
        \centering
    \includegraphics[width=60mm]{./figs/proposition.png}
    \caption{Interface for the supervisor with an action being proposed, moving
        the eagle to the rat with highlight of the eagle and the rat.}
        \label{fig:gui}
\end{figure}
